%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer - Account and Identity Management} % Job title
    {Lexmark International, Inc.} % Organization
    {Lexington, KY} % Location
    {May. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for maintaining a variety of applications that facilited account management, authentication, and identity federation for our cloud services.}
        \item {Facilitated the transition to Azure B2C identity management service from our in-house Ruby on Rails identity provider.}
        \item {Developed serveral customer facing Angular UI's and C\# services and their deployment to our Kubernetes environment.}
        \item {Helped transition serveral services from AWS EKS to Azure AKS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Rotation Program} % Job title
    { } % Organization
    { } % Location
    {Jul. 2018 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {During this program I spent 8 months on 3 different teams in the organization.}
        \item {On the Core Team, I helped to design and build fully automated CI/CD Jenkins pipelines to support the transition of our suite of dockerized microservices to Kubernetes from AWS ECS as well as maintain several Java libraries and SpringBoot services.}
        \item {On the Firmware Security Team, I worked to handle incoming critical CVE's in our firmware, as well as develop a service on our devices that enables automatic updating of critical SSL certificates for authentication with Lexmark and 3rd-party servers.}
        \item {On the Cloud Solutions Team, I created a feature using Azure Device Streams that would allow remote access to IoT devices in our cloud system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PPQA Tools Team Intern} % Job title
    { } % Organization
    { } % Location
    {Aug. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a suite of python scripts that collect usage data from multiple data sources to detect supply failures and end of life.}
%        \item {Built a C\# desktop application, and companion command line tool, to analyze binary packet data.}
%        \item {Designed a basic VR experience to manipulate a 3D model for showcases.}
        \item {Used machine learning to train a model that could identify print errors in QA tests.}
        \item {Developed a logging pipeline utilizing HyperLedger Fabric blockchain and ActiveMq.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
