%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Organizer} % Affiliation/role
    {Lexmark International, Inc. Hackathon} % Organization/group
    {Lexington, KY} % Location
    {2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organized a company wide hackathon that took place over the course of a week.}
        \item {Involved working with multiple levels of management for approval and funding.}
        \item {Held several technical events throughout the week, including sponsored talks and creative events.}
	\item {Week long event cumulated in a final showcase for all projects and a presentation by the winners.}
	\item {Awarded the Manager Appreciation Award as recognition for the effort put into organizing the event.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Hackathons} % Organization/group
    {Kentucky} % Location
    {2016 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in various national level hackathon events during my college career including CatHacks and DerbyHacks.}
	\item {Award winning projects include an automated smart home using a Raspberry Pi, a personal nurse skill for Amazon Alexa, and a semantic analysis engine.}
      \end{cvitems}
    }

%---------------------------------------------------------
\iffalse
  \cventry
    {Member} % Affiliation/role
    {Competative Programming Team} % Organization/group
    {University of Kentucky} % Location
    {Aug. 2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Represented the university in national programming competitions.}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------
\end{cventries}
